A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-04-20 manuscript.Rmd
preregistration as code

>>>>

Often a preregistration is guided by a template, which formalizes the research questions and the planned analysis.
An alternative to such protocol is to submit preregistration as code.
Therefore, instead of describing the analysis that you plan to turn into code and run, you write the code beforehand.
This is obviously challenging to do, because it is so concrete.
